Introduction to\\ Swedish Civil Contingencies Agency (MSB) methodological support for introducing \ac{isms}.

### 2018-04-04 msbframework/msbintro/msbintro.tex
Updated slides with gdpr

% $Id$
%\documentclass[handout]{beamer}
\documentclass{beamer}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[swedish,english]{babel}
\usepackage{url}
\usepackage{graphicx}
\usepackage{color}
\usepackage{subfig}
\usepackage{csquotes}
\usepackage{acro}
\usepackage[natbib,style=alphabetic,maxbibnames=99]{biblatex}
\addbibresource{msbintro.bib}
\DeclareAcronym{isms}
{
  short = ISMS,
  long = Information Security Management Systems,
}

@@

\begin{frame}[allowframebreaks]{Tieto-breakdown}
  \citet{Lindkvist2012tdf} gives the following summary:
  \begin{description}
    \item[Friday afternoon] Tieto notices a disruption in their IT-systems.
      350 pharmacies lost contact with their IT-systems.
      Many larger organisations are also affected, amongst other a larger
      logistical company.

@@

\begin{frame}{Methodological overview}
  \begin{figure}
    \includegraphics[width=\textwidth]{metodstod-overview.png}
    \caption{Overview over the methodological support.}
  \end{figure}
\end{frame}

@@

    \item[Public Access to Information and Secrecy Act 2009:40] Says that certain
      information \emph{must} be available for the public, while other information
      should \emph{not} be.

@@

\begin{frame}{MSBFS 2016:1}
  \begin{itemize}
    \item Due to increased electronic information exchange in the society, there
      is now demands put on how governmental agency work with information
      security.

>>>>

% $Id$
%\documentclass[handout]{beamer}
\documentclass{beamer}
\usepackage[utf8]{inputenc}
\usepackage{lmodern,textcomp}
\usepackage[T1]{fontenc}
\usepackage[swedish,english]{babel}
\usepackage{url}
\usepackage{graphicx}
\usepackage{color}
\usepackage{subfig}
\usepackage{csquotes}
\usepackage{acro}
\usepackage[backend=biber,style=alphabetic,maxbibnames=99]{biblatex}
\addbibresource{msbintro.bib}
\DeclareAcronym{isms}
{
  short = ISMS,
  long = Information Security Management Systems,
}

@@

\begin{frame}[allowframebreaks]{Tieto-breakdown}
  \cite{Lindkvist2012tdf} gives the following summary:
  \begin{description}
    \item[Friday afternoon] Tieto notices a disruption in their IT-systems.
      350 pharmacies lost contact with their IT-systems.
      Many larger organisations are also affected, amongst other a larger
      logistical company.

@@

\begin{frame}{Methodological overview}
  \begin{figure}
    \includegraphics[width=6cm]{metodstod-overview.png}
    \caption{Overview over the methodological support.}
  \end{figure}
\end{frame}

@@

    \item[GDPR] General Data Protection Regulation, Applies in all EU country
      starting from 25th of May 2018.
    \item[Public Access to Information and Secrecy Act 2009:40] Says that certain
      information \emph{must} be available for the public, while other information
      should \emph{not} be.

@@

\begin{frame}{eu:gdpr}{General Data Protection Regulation}
  \begin{itemize}
    \item Replacing Personal Data Act 1998:204
    \item Regulates how personal data are allowed to be stored and used.
      \begin{itemize}
        \item Protects a persons right of privacy\cite[art. 5]{eu:gdpr}
        \item Personal data can only be stored for as long as there is a need
          for it\cite[art. 5]{eu:gdpr}.
      \item Each person must give explicit
        consent to a company/organisation to store, publish or share personal
        data about them\cite[art. 7]{eu:gdpr}.
        \item Ensure that a person have the right to get access to all personal
          data that has been collected about them\cite[art. 15]{eu:gdpr}.
        \item Persons right to erasure\cite[art. 17]{eu:gdpr}. 
      \end{itemize}
  \end{itemize}
\end{frame}
\begin{frame}{GDPR cont.}{General Data Protection Regulation}
    \begin{itemize}
      \item Possibility to transfer personal data (data
          portabililty)\cite[art. 20]{eu:gdpr}.  
      \item Records regarding processing activities must be maintained \cite[art.
        30]{eu:gdpr}.
      \item Personal data breaches must be reported to the supervisory
        authority, without undue delay, not later than 72 hours\cite[art.
        33]{eu:gdpr}.
    \end{itemize}
\end{frame}
\begin{frame}{GDPR cont.}{General Data Protection Regulation}
\begin{itemize}
  \item Data protection by design and default \cite[art. 25]{eu:gdpr}.
      \item Individuals needs to be informed about the personal data
        breach\cite[art. 34]{eu:gdpr}.
    \item An independent agency should ensure that these rules are followed
      \cite[art 51]{eu:gdpr}.
    \item If the organisation does not comply to these regulations, they can be
      fined up to 4\% worldwide turnover or €20 Million, whichever is greater
      \cite[art 83]{eu:gdpr}.
    \item and much more.
\end{itemize}
\end{frame}
\begin{frame}{MSBFS 2016:1}
  \begin{itemize}
    \item Due to increased electronic information exchange in the society, there
      is now demands put on how governmental agency work with information
      security.
